Bayesian statistics and swine flu

### 2009-08-12 docs/pandemic/bayesPandemic.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@356 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{frame}
\frametitle{Severity of infection}

@@

\begin{frame}[fragile]
\frametitle{What we need}
\begin{verbatim}
transition parameter mean sd distribution
InfOns	mean	1	1	gamma	
InfOns	shape	1	1	gamma	
InfOns	zeros	0.1	0.1	beta	
OnsMedM	mean	1	1	gamma	
OnsMedM	shape	1	1	gamma	
OnsMedM	zeros	0.1	0.1	beta	
OnsMedS	mean	1	1	gamma	
OnsMedS	shape	1	1	gamma	
OnsMedS	zeros	0.1	0.1	beta	
OnsMedD	mean	1	1	gamma	
OnsMedD	shape	1	1	gamma	
OnsMedD	zeros	0.1	0.1	beta	
MedRec	mean	1	1	gamma	
MedRec	shape	1	1	gamma	
MedRec	zeros	0.1	0.1	beta	
MedRec	lost	1	1	beta	
\end{verbatim}
\end{frame}

@@

\begin{frame}[fragile]
\frametitle{Simulated data}
<<simData,echo=true,fig=false>>=
params = pandemicParams()
 data = simEpidemic(params, 30)
@
\end{frame}

\begin{frame}
\frametitle{Simulated data}
<<simDataTable,results=tex,fig=false>>=
toPrint = data[1:12,]
toPrint[is.na(toPrint)] = " "
toPrint = as.matrix(toPrint)
latex(toPrint, file="",center="none", title="", table.env=F)
@
\end{frame}

\begin{frame}
\frametitle{Results}

>>>>

\begin{frame}
\frametitle{Types of infection}

@@

\begin{frame}[fragile]
\frametitle{What we need}
\input{bayesPandemicPriors.txt}
\end{frame}

@@

\begin{frame}[fragile]
\frametitle{Simulated data}
<<simData,echo=true,fig=false>>=
params = pandemicParams( 
  MedHospD = c(mean = 1.5, shape = 2, zeros = 0.2)
  )

data = simEpidemic(params, delta=3, days=20)

data[1:10,-1]
@

\begin{frame}[fragile]
\frametitle{Results}
<<mcmcResults,echo=true,fig=false>>=
paramSample = mcmcPandemic(data,params,priors,sigma=0.1,runs=100)
dim(paramSample)
colnames(paramSample)
@
\end{frame}

\begin{frame}
\frametitle{}
\begin{block}{trace plots}
<<tracePlot>>=
plot(paramSample[,"probs.D"], type="l")
@
\end{block}
